Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-03 kappa.tex
Add figures in model set-up.

The simulations presented in this thesis use Parallel Ice Sheet Model (PISM),
an open-source, finite-difference, shallow ice-sheet model
\citep{PISM-authors.2014}. The model reads bedrock topography, sea level,
geothermal heat flux and climate forcing as inputs, and computes the thermal
and dynamic state of the ice sheet, and the associated thermal and
deformational response of an idealised lithosphere. The atmospheric and oceanic
envelopes are not part of the model. However, PISM includes boundary models
that provide simple parametrisations of their effect on the ice model at
supposedly well-defined interfaces (Fig.~??).

\todo{Figure. PISM interfaces}

This section does not attempt to provide an extensive description of PISM,
which can be found in the on-line documentation \citep{PISM-authors.2014}.
Instead, it aims to highlight modelling choices made in the context of this
thesis, and give an overview of the physics involved in these choices.
Notations used and corresponding parameter choices are summarized in Table~??.

@@

\todo{Figure. Ice flow problem sketch}

@@

\todo{Figure. SIA and SSA}

@@

\todo{Figure. SMB model algorithm}

>>>>

The simulations presented in this thesis use Parallel Ice Sheet Model (PISM),
an open-source, finite-difference, shallow ice-sheet model
\citep{PISM-authors.2014}. The model reads bedrock topography, sea level,
geothermal heat flux and climate forcing as inputs, and computes the thermal
and dynamic state of the ice sheet, and the associated thermal and
deformational response of an idealised lithosphere. The atmospheric and oceanic
envelopes are not part of the model. However, PISM includes boundary models
that provide simple parametrisations of their effect on the ice model at
supposedly well-defined interfaces (\cref{fig:model-interfaces}).

This section does not attempt to provide an extensive description of PISM,
which can be found in the on-line documentation \citep{PISM-authors.2014}.
Instead, it aims to highlight modelling choices made in the context of this
thesis, and give an overview of the physics involved in these choices.

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-interfaces}
  \caption{Model interfaces in PISM. From \citet{PISM-authors.2014}.}
  \label{fig:model-interfaces}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{model-variables}
  \caption{Model variables. \todo{This is an old figure which does not match
           with notations in use, just to give an idea. Redraw.}}
  \label{fig:model-variables}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-siassa}
  \caption{The SIA and SSA. From \citet{Winkelmann.etal.2011}. \todo{Redraw.}}
  \label{fig:model-siassa}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{model-pdd}
  \caption{PDD model. From \citet{PISM-authors.2014} \todo{Redraw.}}
  \label{fig:model-pdd}
\end{figure}
